### 2017-06-29 README.Rmd
fi typo

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("manual" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

>>>>

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```
